---
title: "Multi - Network Approach"
author: "Davide Mascolo"
date: "2023-07-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script is used to build different PSN using several sources of data.

### Import Utils
```{r}
## Utils
library(vegan)
library(igraph)
library(gplots)
library(centiserve)
```

### Custom Functions
```{r}
## Function that computes the features from the network
features_extractor <- function(g, strength, closeness = igraph::closeness, 
                     bonanich_centrality, closeness.currentflow,
                     estimate_betweenness,
                     cutoff_bet = 2/vcount(g)*(vcount(g)-1),
                     eigen_centrality, hub_score, authority_score,
                     page_rank, type_of_net){
  ## Input: Graph, Metrics
  ## Output: Dataframe
  
  ## Compute metrics
  ## Weighted Degree
  weighted_degree        <- cbind(strength(g))
  ## Closeness 
  closeness_centrality   <- cbind(closeness(g))
  ## Bonacich Centrality
  bonanich_centrality <- cbind(power_centrality(g,
                                          exponent = -2,
                                          rescale = T))
  ## Current Flow Closeness
  current_flow_closeness <- cbind(closeness.currentflow(g))
  ## Betweenness
  betweenness_centrality <- cbind(estimate_betweenness(g,
                            cutoff = cutoff_bet))
  ## Eigenvector
  eigen_vector_centrality <- cbind(eigen_centrality(g)$vector)
  ## Hub Score
  hub_score               <- cbind(hub_score(g)$vector)
  ## Authority Score
  aut_score               <- cbind(authority_score(g)$vector)
  ## Page Rank
  page_rank_centrality    <- cbind(page_rank(g)$vector)

  ## Organize into dataframe
  df_metrics <- cbind(weighted_degree, closeness_centrality,
                      bonanich_centrality, current_flow_closeness,
                      betweenness_centrality,eigen_vector_centrality,
                      hub_score, aut_score, page_rank_centrality)
  
  ## Set colnames
  colnames(df_metrics) <- c("Weighted_Degree", "Closeness_Centrality",
                            "Bonanich_Centrality","Current_Flow_Closeness",
                            "Betweenness_Centrality",
                            "Eigenvector_Centrality", "Hub_Score",
                            "Authority_Score", "Page_Rank_Centrality")
  ## Control
  if (type_of_net == "wes"){
    colnames(df_metrics) <- paste(colnames(df_metrics),
                                  "_wes", sep = "")}
  else{
    colnames(df_metrics) <- paste(colnames(df_metrics),
                                  "_rna", sep = "")}
    
  return(df_metrics)
}
```


### PSN - WES (Exome) Data
#### Load Data
```{r}
## Load Exome Data
df_wes <- read.csv("wes_counts.csv", header = T)

## Load RNA data
## Response Group
df_response   <- read.csv("df_response_filtered.csv",
                          header = T)
## Resistance Group
df_resistance <- read.csv("df_resistance_filtered.csv",
                          header = T)

## Load list of 10% hubs
hubs_10 <- readLines("10%_hubs_diff_coex_raw.txt")
```

#### Data Wrangling
```{r}
## Set index
rownames(df_wes) <- df_wes$Tumor_Sample_Barcode
df_wes$Tumor_Sample_Barcode <- NULL

## Create complete dataset
df_rna <- cbind(df_response, df_resistance)
## Set index
rownames(df_rna) <- df_rna$X
df_rna$X <- NULL
df_rna$X <- NULL

## Subset
df_hubs_10 <- subset(df_rna, rownames(df_rna) %in%
                       hubs_10)
## Check
df_hubs_10 <- t(df_hubs_10)

## Filter wes data wrt the patients that are in rna data
## Save list of patients
patients_list <- rownames(df_hubs_10) <- gsub("\\.", "-", rownames(df_hubs_10))
## Filter
df_wes_filtered <- df_wes[rownames(df_wes) %in% patients_list, ]
```

```{r}
## Check
message("WES data shape:")
dim(df_wes_filtered)

## Check if there are Na
message("WES data NaN:")
table(is.na(df_wes_filtered))

## Check if there are some values that are different from 0 and 1
message("Check if there are some values that are different from 0 and 1:")
any(df_wes_filtered != 0 & df_wes_filtered != 1)

## Check
message("Number of 10% genes: ")
length(hubs_10)
```


#### Network
```{r}
## Implement the network using Binary distance
## It's possible to try also with different measures like Hamming distance
#bin_sim <- as.matrix(1 / (1+dist(df_wes_filtered, method = "binary")))
hamming_wes_dist <- as.matrix(1 / (1+Mercator::binaryDistance(t(df_wes_filtered), "hamming")))

## Set to 0 the diagonal of the matrix
diag(hamming_wes_dist) <- 0

## We implement the network
psn_wes <- graph.adjacency(hamming_wes_dist,
                           mode = "undirected",
                           weighted = TRUE)
```

```{r}
## Plot Heatmap
heatmap.2(hamming_wes_dist,
          main = "Heatmap using Hamming Similarity on WES data",
          margins = c(10, 10))
```

```{r}
## Louvian Algorithm for Community Detection
community_wes_louvian <- cluster_louvain(psn_wes)
```

### PSN - RNA Data
```{r}
## Compute Euclidean Similarity
dist_rna <- as.matrix(1 / (1+dist(df_hubs_10, method = "maximum")))

## Set to 0 the diagonal of the matrix
diag(dist_rna) <- 0

## We implement the network
psn_rna <- graph.adjacency(dist_rna,
                           mode = "undirected",
                           weighted = TRUE)
```

```{r}
## Plot Heatmap
heatmap.2(dist_eucl_hubs_10,
          main = "Heatmap using Maximum Similarity on RNA data, with 10% Hubs Co-Expression Network",
          margins = c(10, 10))
```

```{r}
## Louvian Algorithm for Community Detection
community_rna_louvian <- cluster_louvain(psn_rna)
```


#### Centrality Features Extraction
```{r}
## From the PSNs it's possible to extract two types of features:
## 1. centrality features
## 2. modularity features

## List of all the metrics
## strength, closeness = igraph::closeness, bonanich_centrality, closeness.currentflow, estimate_betweenness, cutoff, eigen_centrality, hub_score, authority_score, page_rank, type_of_net


## Apply the function to extract features
## Features PSN WES
df_wes_features <- features_extractor(psn_wes, strength,
                   closeness = igraph::closeness, 
                   bonanich_centrality, closeness.currentflow,
                   estimate_betweenness,
                   cutoff_bet = 2/vcount(psn_wes)*(vcount(psn_wes)-1),
                   eigen_centrality, hub_score, authority_score,
                   page_rank, type_of_net = "wes")

## Features PSN RNA
df_rna_features <- features_extractor(psn_rna, strength,
                   closeness = igraph::closeness, 
                   bonanich_centrality, closeness.currentflow,
                   estimate_betweenness,
                   cutoff_bet = 2/vcount(psn_rna)*(vcount(psn_rna)-1),
                   eigen_centrality, hub_score, authority_score,
                   page_rank, type_of_net = "rna")
```

```{r}
## Check 
message("df wes data shape:")
dim(df_wes_features)
message("df rna data shape:")
dim(df_rna_features)
```

```{r}
## Check
View(df_wes_features);View(df_rna_features)
```

```{r}
## Merge
df_final_features_centrality <- rbind(df_wes_features, df_rna_features)
## Set colnames
colnames(df_final_features_centrality) <- gsub("_wes", "",
                                    colnames(df_final_features_centrality))
## Check
message("df merged shape:")
dim(df_final_features_centrality)
```

```{r}
## Save
write.csv(df_final_features_centrality, "df_final_centrality_wes_rna.csv")
```


#### Community Detection
```{r}
## Compute other communities for wes and rna data

## WES
## 1. Edge-Betweenness
community_wes_betweenness <- cluster_edge_betweenness(psn_wes)
## 2. Label-Propagation
community_wes_propagation <- cluster_label_prop(psn_wes)
## 3. Walktrap
community_wes_walktrap    <- cluster_walktrap(psn_wes)
## 4. Infomap
community_wes_infomap     <- cluster_infomap(psn_wes)

## RNA
## 1. Edge-Betweenness
community_rna_betweenness <- cluster_edge_betweenness(psn_rna)
## 2. Label-Propagation
community_rna_propagation <- cluster_label_prop(psn_rna)
## 3. Walktrap
community_rna_walktrap    <- cluster_walktrap(psn_rna)
## 4. Infomap
community_rna_infomap     <- cluster_infomap(psn_rna)
```

#### Check Modularity
```{r}
## Modularity WES Data
message("Modularity WES data: ")
message("\n")
message("Modularity Louvian")
modularity(community_wes_louvian)
message("Modularity Edge-Betweenness")
modularity(community_wes_betweenness)
message("Modularity Label-Propagation")
modularity(community_wes_propagation)
message("Modularity Walktrap")
modularity(community_wes_walktrap)
message("Modularity Infomap")
modularity(community_wes_infomap)
message("\n")

## Modularity RNA Data
message("Modularity RNA data: ")
message("\n")
message("Modularity Louvian")
modularity(community_rna_louvian)
message("Modularity Edge-Betweenness")
modularity(community_rna_betweenness)
message("Modularity Label-Propagation")
modularity(community_rna_propagation)
message("Modularity Walktrap")
modularity(community_rna_walktrap)
message("Modularity Infomap")
modularity(community_rna_infomap)
```

#### Check Communities
```{r}
## How many communities?

message("Communities WES data: ")
message("\n")
message("Communities Louvian")
length(unique(community_wes_louvian$membership))
message("Communities Edge-Betweenness")
length(unique(community_wes_betweenness$membership))
message("Communities Label-Propagation")
length(unique(community_wes_propagation$membership))
message("Communities Walktrap")
length(unique(community_wes_walktrap$membership))
message("Communities Infomap")
length(unique(community_wes_infomap$membership))
message("\n")

message("Communities RNA data: ")
message("\n")
message("Communities Louvian")
length(unique(community_rna_louvian$membership))
message("Communities Edge-Betweenness")
length(unique(community_rna_betweenness$membership))
message("Communities Label-Propagation")
length(unique(community_rna_propagation$membership))
message("Communities Walktrap")
length(unique(community_rna_walktrap$membership))
message("Communities Infomap")
length(unique(community_rna_infomap$membership))
```

Looking these results (modularity), Louvian and Walktrap algorithms were choosen for extract modularity features.

#### Extract Modularity Memberships Features
```{r}
## WES Data
membership_wes_louvian  <- cbind(membership(community_wes_louvian))
membership_wes_walktrap <- cbind(membership(community_wes_walktrap))
## Set colnames
df_membership_wes_features <- cbind(membership_wes_louvian,
                                    membership_wes_walktrap)
colnames(df_membership_wes_features) <- c("Louvian_wes",
                                          "Walktrap_wes")

  
## RNA Data
membership_rna_louvian  <- cbind(membership(community_rna_louvian))
membership_rna_walktrap <- cbind(membership(community_rna_walktrap))
## Set colnames
df_membership_rna_features <- cbind(membership_rna_louvian,
                                    membership_rna_walktrap)
colnames(df_membership_rna_features) <- c("Louvian_rna",
                                          "Walktrap_rna")
```

```{r}
## Check
message("WES Modularity Shape:")
dim(df_membership_wes_features)
message("RNA Modularity Shape:")
dim(df_membership_rna_features)

## Combine
df_final_features_modularity <- rbind(df_membership_wes_features,
                                      df_membership_rna_features)
colnames(df_final_features_modularity) <- c("Louvian",
                                            "Walktrap")
## Convert to df
df_final_features_modularity <- as.data.frame(df_final_features_modularity)
rownames(df_final_features_modularity) <- gsub("\\.",
                      "-", rownames(df_final_features_modularity))
  
## Check
message("df merged shape:")
dim(df_final_features_modularity)
```
```{r}
## The final step is merge the two dataframe and use the final as input for the classifier
message("df centrality shape:")
dim(df_final_features_centrality)

message("df modularity shape:")
dim(df_final_features_modularity)


## Save
write.csv(df_final_features_modularity, "df_final_modularity_wes_rna.csv")
```

```{r}
## Join
df_final_wes_rna <- df_final_features_centrality
df_final_wes_rna <- as.data.frame(df_final_wes_rna)          
df_final_wes_rna$Louvian  <- df_final_features_modularity$Louvian
df_final_wes_rna$Walktrap <- df_final_features_modularity$Walktrap

## Set rownames
rownames(df_final_wes_rna) <- gsub("\\.",
                      "-", rownames(df_final_wes_rna))

## Chedk
message("df final shape:")
dim(df_final_wes_rna)


## Save
write.csv(df_final_wes_rna, "df_final_wes_rna.csv")
```