---
title: "Similarity Network Fusion (SNF) - All Genes"
author: "Davide Mascolo"
date: "2023-09-06"
output: html_document
---

## Utils
```{r setup, include = FALSE}
library(tidyverse)
library(SNFtool)
library(e1071)
library(ggplot2)
library(readxl)
library(flexclust)
library(glue)
library(igraph)
library(gplots)
library(caret)
library(stats)
library(ggsurvfit)
library(survival)
```

## Custom Functions
```{r}
## Create a function that returns the string in correct form
clean_patient <- function(patients_list){
  ## Input: list of patients code to format
  ## Output: code formatted
  return(gsub("\\.", "-", patients_list))
}

optimal_cluster <- function(affinity_matrix, C, label){
  ## Create an empty lists to save NMI values
  NMI_values     <- list()
  ## Define an empty dataframe where to collect the final result
  df_cluster <- data.frame(K = c(C),
                           NMI = rep(0, length(C))) 
  ## Compute clustering
  for (i in C){
    cluster    <- spectralClustering(affinity_matrix, K = i)
    ## Plot
    displayClustersWithHeatmap(affinity_matrix, cluster,
                               main = glue("Clustering with K = {i}"))
    NMI_values <- append(NMI_values, calNMI(cluster, label))}
  df_cluster$NMI <- NMI_values
  return(df_cluster)
}
```

## Load Data
```{r}
## Set path
path <- getwd()

## Load Data

## Rna Gene Counts (consider all the genes not only the DEGs)
df_rna_counts <- read.csv(paste0(path, "/Data/rna_counts.csv"))

## Exome (WES - Consider all possible genes, not only driver genes) 
df_wes <- read.csv(paste0(path, "/Data/Exome_genes.csv"))

## Clinical
df_clinical <- read_excel(paste0(path, "/Data/SU2C-MARK_Supplementary_Tables_Combined_v5_Filtered.xlsx"),
                         sheet = "Table_S1_Clinical_Annotations",
                         skip = 2)


## Some pre-processing

## Rna Gene Counts
df_rna_counts$Name        <- NULL
gene_names                <- df_rna_counts$Description
df_rna_counts$Description <- NULL
colnames(df_rna_counts)   <- clean_patient(colnames(df_rna_counts))
df_rna_counts             <- data.frame(t(df_rna_counts))
colnames(df_rna_counts)   <- gene_names

## Exome
wes_patients     <- df_wes$Tumor_Sample_Barcode
rownames(df_wes) <- clean_patient(wes_patients)
df_wes           <- df_wes[,-2]
df_wes$X         <- NULL

## Clinical data
df_clinical$Harmonized_SU2C_Participant_ID_v2 <- paste(
  df_clinical$Harmonized_SU2C_Participant_ID_v2, "T1", sep = "-")
```

So, at the end of the story the following integration will be considered:
- RNA-Seq Data
- Exome Data

## Data Wrangling
```{r}
## Check
dim(df_rna_counts);dim(df_wes)
```

```{r}
## At this point, is possible to filter the patients of WES data using the patients that are in RNA-Seq data.

## Number of patients in common: 65
common_patients <- intersect(rownames(df_rna_counts),
                             rownames(df_wes))

## Filter the dataframe with two different sets of patients
## Rna Counts
df_rna_counts_final <- df_rna_counts[rownames(df_rna_counts) %in%
                                       common_patients,]
dim(df_rna_counts_final)
## Dim: 65 patients x 57523 genes

## Wes
df_wes_final        <- df_wes[rownames(df_wes)
                              %in% common_patients,]
dim(df_wes_final)
## Dim: 65 patients x 16270 genes

## Extract true label
## RNA
df_clinical_filter <- df_clinical %>% 
  select(Harmonized_SU2C_Participant_ID_v2,
         Harmonized_Confirmed_BOR,
         Patient_Age_at_Diagnosis, Patient_Sex,
         Harmonized_PFS_Event, Harmonized_PFS_Days,
         Harmonized_OS_Event, Harmonized_OS_Days,
         Harmonized_Confirmed_BOR, Initial_Stage,
         Patient_Race, Patient_Smoking_Status,
         Histology_Harmonized, Line_of_Therapy,
         Agent_PD1_Category) %>% 
  filter(Harmonized_SU2C_Participant_ID_v2 %in% common_patients)
true_label <- df_clinical_filter$Harmonized_Confirmed_BOR

## Format
true_label <- case_when(true_label == "PR" ~ 1,
                        true_label == "PD" ~ 2,
                        true_label == "SD" ~ 2,
                        TRUE ~ 1)
```

```{r}
## Check
dim(df_rna_counts_final);dim(df_wes_final)
```

## SNF
### Compute distances
In this chunk is possible to compute matrices for both datasets. Here we use the default euclidian distance for RNA-Seq data and the hamming distance for WES data.
```{r}
## Scaling
## RNA-Seq
df_rna_counts_scaled <- standardNormalization(df_rna_counts_final)
## WES
df_wes_scaled        <- df_wes_final  

## Compute distances
## RNA-Seq
dist_rna_counts  <- (dist2(as.matrix(df_rna_counts_scaled),
                           as.matrix(df_rna_counts_scaled)))^(1/2)
## WES
dist_wes         <- (dist2(as.matrix(df_wes_scaled),
                           as.matrix(df_wes_scaled),
                           method = "binary"))^(1/2)
```

```{r}
## Check
dim(dist_rna_counts)[1] == dim(df_rna_counts_scaled)[1]
dim(dist_wes)[1]        == dim(df_wes_scaled)[1]
```


### Affinity Matrix
To convert distance matricies to similarity matricies, is possible to use affinityMatrix, which takes three arguments:
- distance matrix
- k: the number of neighbours, where affinities outsied of the neighbourhouud are set to zero (10~30)
- sigma: is the hyperparameter for the scaled exponential similarity kernel used to conduct the acual affinity calculation. Both of these parameters are chosen empirically. (0.3~0.8)
- T: number of iterations. (10~30)

```{r}
## Parameters
C <- 3
K <- 5
t <- 20
alpha <- 0.8
```

```{r}
## Affinity Matrix
W_1 <- affinityMatrix(dist_rna_counts, K = K, sigma = alpha)
W_2 <- affinityMatrix(dist_wes, K = K, sigma = alpha)
```

### Spectral Clustering
```{r}
## Clustering
cluster_rna_counts <- optimal_cluster(W_1, C, true_label)
cluster_wes        <- optimal_cluster(W_2, C, true_label)

## SPectral Clustering
cluster_rna_counts_final <- spectralClustering(W_1, K = C)
cluster_wes_final        <- spectralClustering(W_2, K = C)
```
```{r}
## Save the patients for each community
## RNA-Seq
communities_rna <- data.frame(ID_Patient = c(common_patients),
                  Community = c(cluster_rna_counts_final),
                  Response = c(true_label),
                  Sex = df_clinical_filter$Patient_Sex,
                  Time = df_clinical_filter$Harmonized_OS_Days)
## WES
communities_wes <- data.frame(ID_Patient = c(common_patients),
                   Community = c(cluster_wes_final),
                   Response = c(true_label),
                   Sex = df_clinical_filter$Patient_Sex,
                   Time = df_clinical_filter$Harmonized_OS_Days)

## RNA-Seq Data
## Patients who are Response in different communities
resp_rna_comm_01 <- communities_rna %>%
  filter(Response == 1 & Community == 1) %>% 
  count()
resp_rna_comm_02 <- communities_rna %>%
  filter(Response == 1 & Community == 2) %>% 
  count()
resp_rna_comm_03 <- communities_rna %>%
  filter(Response == 1 & Community == 3) %>% 
  count()
## Number of patients for each community
n_comm_01_rna <- communities_rna %>%
  filter(Community == 1) %>% 
  count()
n_comm_02_rna <- communities_rna %>%
  filter(Community == 2) %>% 
  count()
n_comm_03_rna <- communities_rna %>%
  filter(Community == 3) %>% 
  count()
## Total Number of Response patients
response_patients <- true_label[true_label == 1]
  


## WES Data
## Patients who are Response in different communities
resp_wes_comm_01 <- communities_wes %>%
  filter(Response == 1 & Community == 1) %>% 
  count()
resp_wes_comm_02 <- communities_wes %>%
  filter(Response == 1 & Community == 2) %>% 
  count()
resp_wes_comm_03 <- communities_wes %>%
 filter(Response == 1 & Community == 3) %>% 
  count()
## Number of patients for each community
n_comm_01_wes <- communities_wes %>%
  filter(Community == 1) %>% 
  count()
n_comm_02_wes <- communities_wes %>%
  filter(Community == 2) %>% 
  count()
n_comm_03_wes <- communities_wes %>%
  filter(Community == 3) %>% 
  count()
```

### Fusion Network
It's possible to see both matricies have some information about clusters in them. 
```{r}
## Fusion algorithm
W <- SNF(list(W_1, W_2), t, t)

## Clustering with best C <- 3
final_clusters <- spectralClustering(W, K = C)

## Plot
displayClustersWithHeatmap(W,
              spectralClustering(W, K = C)) ## To analyze using clinical features (EDA)

## Evaluate
calNMI(final_clusters, true_label)
```

It's also possible to find the concordance between each individual network and the fused network
```{r}
## Concordance Matrix
(concordance_matrix      <- concordanceNetworkNMI(list
                                (W, W_1, W_2), C))
## This output shows the concordance between the fused network and each individual network.
```
How many patients Response/Non-Response are in the different clusters?
```{r}
## Save the patients for each community
communities <- data.frame(ID_Patient = c(common_patients),
                          Community = c(final_clusters),
                          Response = c(true_label),
                  Sex = df_clinical_filter$Patient_Sex,
                  Time = df_clinical_filter$Harmonized_OS_Days)
communities <- na.omit(communities)
## Remember: True_Label = 1 --> Response
##           True_Label = 2 --> Resistance

## Check
dim(communities);View(communities)
```

## Plot
```{r}
## Community
ggplot(communities, aes(x = Community, y = after_stat(count))) +
  geom_bar(color = "steelblue", fill = "steelblue") +
  ggtitle(label = "Clusters Distribution",
          subtitle = "for Similarity Network Fusion") +
  ylab("N.") +
  theme_grey()
```

We can conduct between-group significance tests using a log-rank test. The log-rank test equally weights observations over the entire follow-up time and is the most common way to compare survival times between groups.
```{r}
## Difference wrt Community
model_fit <- survdiff(Surv(Time, Response) ~ Community,
                      data = communities)

## Plot
survfit2(Surv(Time, Response) ~ Community,
         data = communities) %>% 
  ggsurvfit(lwd = 1.3) +
  labs(x = "Days", y = "Overall Survival Probability",
       title = "Survival Plot") + ## basic plot
  add_risktable()           + ## numbers at risk
  add_legend_title("Community") +
  theme_gray() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

## Check
model_fit
```

The following hypotheses are used in this test:

H0: There is no difference in survival between the groups.

H1: There is a difference in survival between the groups.

With two degree of freedom, the Chi-Squared test statistic is 1, and the associated p-value is 0.6. We CANNOT REJECT the null hypothesis because the p-value is not smaller than 0.05.


## Enrichment Clusters Analysis (Hypergeometric Distribution)
```{r}
## Patients who are Response in different communities
resp_snf_comm_01 <- communities %>%
  filter(Response == 1 & Community == 1) %>% 
  count()
resp_snf_comm_02 <- communities %>%
  filter(Response == 1 & Community == 2) %>% 
  count()
resp_snf_comm_03 <- communities %>%
  filter(Response == 1 & Community == 3) %>% 
  count()
## Number of patients for each community
n_comm_01_snf <- communities %>%
  filter(Community == 1) %>% 
  count()
n_comm_02_snf <- communities %>%
  filter(Community == 2) %>% 
  count()
n_comm_03_snf <- communities %>%
  filter(Community == 3) %>% 
  count()
```

Idea: Data un'urna con N biglie(popolazione di riferimento, 65), di cui K rosse(risposta, 29) e N-K verdi(non risposta, 36). Se estraiamo n biglie(numerosità community), qual è la probabilità di estrarre esattamente k biglie rosse(risposta)?
```{r}
## How to use the function:
## x: number of successes in the community
## m: number of successes in the population
## n: population size - m
## k: sample size

## Hypergeometric Distribution
## Response (RNA)
print("RNA Clusters")
## Community 01
print("Community 01:")
phyper(16, 29, 65-29, 35)
## Community 02
print("Community 02:")
phyper(13, 29, 65-29, 30)
## Community 03
print("Community 03:")
phyper(1, 29, 65-29, 38)

## Response (WES)
print("WES Clusters")
## Community 01
print("Community 01:")
phyper(12, 29, 65-29, 39)
## Community 02
print("Community 02:")
phyper(17, 29, 65-29, 26)
## Community 03
print("Community 03:")
phyper(5, 29, 65-29, 21)

## Response (SNF)
print("SNF Clusters:")
## Community 01
print("Community 01:")
phyper(17, 29, 65-29, 39)
## Community 03
print("Community 03:")
phyper(16, 29, 65-29, 26)
```

```{r}
## For each cluster save the list of patients
## Community 01
community_01 <- communities %>% 
  filter(Community == 1)
## Community 02
community_02 <- communities %>% 
  filter(Community == 2)
## Community 03
community_03 <- communities %>% 
  filter(Community == 3)

## Save
write.csv(community_01, paste0(path, "/Clusters/community_01.csv"),
          row.names = F)
write.csv(community_02, paste0(path, "/Clusters/community_02.csv"),
          row.names = F)
write.csv(community_03, paste0(path, "/Clusters/community_03.csv"),
          row.names = F)
```

Use label propagation to predict the labels of new data points.
```{r}
## Predictions

## Create training and test data
n            <- floor(0.6 * length(true_label)) ## training samples
train_sample <- sample.int(length(true_label), n) 
x_train      <- lapply(W, function(x) W[train_sample, ])
x_test       <- lapply(W, function(x) W[-train_sample, ])
groups       <- true_label[train_sample]
```

```{r}
## Parameters
K      <- 10
alpha  <- 0.2
t      <- 20
method <- T
```

```{r}
## Apply prediction
y_pred <- groupPredict(x_train, x_test, groups, K, alpha, method)
```

```{r}
## Evaluate computing the accuracy
(accuracy  <- sum(true_label[-train_sample] == y_pred[-c(1:n)])/
   (length(true_label) - n))
```
