---
title: "Data Preparation"
author: "Davide Mascolo"
date: "2023-05-26"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import Utils and Setup
```{r}
set.seed(123)
library(magrittr)
library(data.table)
library(tidyverse)
library(readxl)
library(dplyr)
```

## Load Data
The following datasets are loaded: 1. Clinical Table Annotations 2. RNA Counts 3. RNA Log Counts
```{r}
## Load Directory
source_data_path <- getwd()

## Load Gene Names file
load(paste0(source_data_path, "/gene_names.rds"))

## Load Clinical Table Annotation
master_annotations_df <- read_excel(paste0(source_data_path,
                                           "/Table_S1_Clinical_Annotations.xlsx"),
                                    sheet = "Table_S1_Clinical_Annotations",
                                    skip = 2)

## Load RNA Counts
su2c_rna_counts_mat <-  read_delim(paste0(
  source_data_path,"/SU2C-MARK_Supplementary_Table_12_RNA_Counts_v4.gct"),
  skip = 2)
## Set row names
row.names(su2c_rna_counts_mat) <- su2c_rna_counts_mat$Name

## Load log RNA Counts
su2c_rna_log2tpm_mat <- read_delim(paste0(
  source_data_path, "/SU2C-MARK_Supplementary_Table_14_RNA_TPM.gct"),
  skip = 2)
## Set row names
row.names(su2c_rna_log2tpm_mat) <- su2c_rna_log2tpm_mat$Name
```

### Description of data
```{r}
## Check Clinical table
dim(master_annotations_df)
## Check RNA Counts
dim(su2c_rna_counts_mat)
## Check RNA Log Counts 
dim(su2c_rna_log2tpm_mat)
```

### View
```{r}
## Clinical table
View(master_annotations_df)
## RNA Counts
View(su2c_rna_counts_mat[1:20, 1:20])
## RNA Log Counts
View(su2c_rna_log2tpm_mat[1:20, 1:20])
```

## Data Wrangling

For this part, we consider the feature **Pre-treatment_RNA_Sample_QC** that contains information about **Tumor RNA-Seq sample quality**. For the whole dataset, the number of patients is 393, but for the DEG analysis we consider only the patients with highest quality of RNA samples. So, the feature defined contains different NaN.

```{r}
## Check NaN
table(is.na(master_annotations_df$`Pre-treatment_RNA_Sample_QC`))
```

We consider only the 152 observations that are divided in the following way:

```{r}
## Count the different levels of 152 obsevrations
table(master_annotations_df$`Pre-treatment_RNA_Sample_QC`)
```

```{r}
## Filter by QC
rna_master_annotations_df <-
  master_annotations_df[master_annotations_df$`Pre-treatment_RNA_Sample_QC` == "Keep" | master_annotations_df$`Pre-treatment_RNA_Sample_QC` == "Flag",]

## Format 
all_rna_samples <- as.character(na.omit(rna_master_annotations_df$Harmonized_SU2C_RNA_Tumor_Sample_ID_v2) )

## Select
## N.B.: all_rna_samples is a list that contains all the patients with the
## highest quality sample
rna_counts_mat            <- su2c_rna_counts_mat[, all_rna_samples]
row.names(rna_counts_mat) <- row.names(su2c_rna_counts_mat)
## Check
dim(rna_counts_mat)
## Save
write.csv(rna_counts_mat, row.names = TRUE,
          paste0(source_data_path,
                 "/rna_counts_mat.csv"))
```

The final table is organized in the following way:
- for each row: gene
- for each column: patient

```{r}
## View
head(rna_counts_mat[1:10, 1:10])
```

The same operation is done also for RNA log Counts
```{r}
## Apply
rna_log2tpm_mat            <- su2c_rna_log2tpm_mat[, all_rna_samples]
row.names(rna_log2tpm_mat) <- row.names(su2c_rna_log2tpm_mat)
rna_log2tpm_mat            <- log2(rna_log2tpm_mat + 1)
## Check
dim(rna_log2tpm_mat)
## Save
write.csv(rna_log2tpm_mat, row.names = FALSE,
          paste0(source_data_path,
                 "/rna_log2tpm_mat.csv"))
```

Now, we filter out the samples that have mixed small-cell histology
```{r}
## Training (RNA_Cohort_1 == 1)
rna_training_samples <-
  as.character(na.omit(
    rna_master_annotations_df$Harmonized_SU2C_RNA_Tumor_Sample_ID_v2[
      rna_master_annotations_df$RNA_Cohort_1 == 1]))
## 122 samples

## Validation (RNA_Cohort_2 == 1)
rna_validation_samples <-
  as.character(na.omit(
    rna_master_annotations_df$Harmonized_SU2C_RNA_Tumor_Sample_ID_v2[
      rna_master_annotations_df$RNA_Cohort_2 == 1]))
## 30 samples

## Set diff
rna_training_samples     <- setdiff(rna_training_samples, c("SU2CLC-MGH-1151-T1"))
training_rna_log2tpm_mat <- rna_log2tpm_mat[, rna_training_samples]
row.names(training_rna_log2tpm_mat) <- row.names(rna_log2tpm_mat)
## Save
write.csv(training_rna_log2tpm_mat, row.names = FALSE,
          paste0(source_data_path,
                 "/training_rna_log2tpm_mat.csv"))
```

```{r}
## Set aside validation + flagged input for BNMF

## RNA Validation Samples is composed by:
## samples with RNA_Cohort_2 == 1
## samples with QC == Flag
rna_validation_flag_samples <- union(
  rna_validation_samples,
  na.omit(rna_master_annotations_df$Harmonized_SU2C_RNA_Tumor_Sample_ID_v2[
    rna_master_annotations_df$`Pre-treatment_RNA_Sample_QC` == "Flag"]))

## Log RNA Validation Samples
validation_rna_log2tpm_mat <- rna_log2tpm_mat[,
as.character(rna_validation_flag_samples)]
validation_rna_log2tpm_df <- as.data.frame(validation_rna_log2tpm_mat) %>%
  mutate(ensembl_gene_id_version = rownames(validation_rna_log2tpm_mat))
validation_rna_log2tpm_df <- validation_rna_log2tpm_df[,c("ensembl_gene_id_version", rna_validation_flag_samples)]

## Save
write.csv(validation_rna_log2tpm_df, row.names = FALSE,
          paste0(source_data_path,
                 "/SU2C_validation+flag.classifier.input.csv"))
```