---
title: "Survival Analysis"
author: "Davide Mascolo"
date: "2023-07-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Import Utils
```{r}
## Libraries
library(dplyr)
library(tidyverse)
library(survival)
library(ggsurvfit)
library(gtsummary)
library(tidycmprsk)
library(sm)
library(zoo)
library(condsurv)
library(kableExtra)
library(survminer)
```

### Load Data
```{r}
## Clinical Data
df_annotation <- read.csv("master_annotation.csv",
                          header = T)
df_annotation$X <- NULL
```

```{r}
## Check
dim(df_annotation);View(df_annotation)
```

Features that we need:
1. time: Observed survival times in days
2. status: censoring status 1 = censored, 2 = dead
3. sex: 1 = Male, 2 = Female
4. response: 1 = Partial Response, 2 = Complete Response,
             3 = Stable Disease, 4 = Progression Disease
             
NB:  Progression-free survival (PFS), the time from treatment initiation until disease progression or worsening, may be used as a direct or surrogate measure of clinical benefit for drug approvals, depending on the disease and response observed, while overall survival (OS), the duration of patient survival from the time of treatment initiation, is a universally-accepted direct measure of clinical benefit.

### Data Wrangling
```{r}
## Select only some features
df_annotation_part_1 <- df_annotation %>% 
  select(Harmonized_SU2C_Participant_ID_v2,
         Patient_Age_at_Diagnosis, Patient_Sex,
         Harmonized_PFS_Event, Harmonized_PFS_Days,
         Harmonized_OS_Event, Harmonized_OS_Days,
         Harmonized_Confirmed_BOR, Initial_Stage,
         Patient_Race, Patient_Smoking_Status,
         Histology_Harmonized, Line_of_Therapy,
         Agent_PD1_Category)

## Create new column for response
df_annotation_part_1 <- df_annotation_part_1 %>% 
  mutate(Response = case_when(
    Harmonized_Confirmed_BOR == "PR" ~ 1,
    Harmonized_Confirmed_BOR == "CR" ~ 2,
    Harmonized_Confirmed_BOR == "SD" ~ 3,
    Harmonized_Confirmed_BOR == "PD" ~ 4,
    TRUE ~ NA_integer_))
```

```{r}
## Check
dim(df_annotation_part_1);View(df_annotation_part_1)
```
```{r}
## Mutate some features

## Harmonized OS Event
df_annotation_part_1$Harmonized_OS_Event <- ifelse(df_annotation_part_1$Harmonized_OS_Event == 0, 1, 2)

## Patient Sex
df_annotation_part_1$Patient_Sex <- ifelse(df_annotation_part_1$Patient_Sex == "M", 1, 2)
```

```{r}
## Check
table(df_annotation$Harmonized_OS_Event)
table(df_annotation_part_1$Harmonized_OS_Event)

## Check
table(df_annotation$Patient_Sex)
table(df_annotation_part_1$Patient_Sex)

## Check
table(df_annotation$Harmonized_Confirmed_BOR)
table(df_annotation_part_1$Harmonized_Confirmed_BOR)
```

```{r}
## Organize the final df

## Rename time column
colnames(df_annotation_part_1)[colnames(df_annotation_part_1) == "Harmonized_OS_Days"] <- "Time"

## Rename status column
colnames(df_annotation_part_1)[colnames(df_annotation_part_1) == "Harmonized_OS_Event"] <- "Status"

## Rename Sex column
colnames(df_annotation_part_1)[colnames(df_annotation_part_1) == "Patient_Sex"] <- "Sex"
```

```{r}
## Select only the features of interest
df_annotation_part_1_final <- df_annotation_part_1 %>% 
  select(Time, Status, Sex, Response)
## Check
head(df_annotation_part_1_final)
## Remove NaN
df_annotation_part_1_final <- na.omit(df_annotation_part_1_final)
```

### Part 1 - Survival Analysis
```{r}
## Compute survival times
head(Surv(df_annotation_part_1_final$Time,
          df_annotation_part_1_final$Status), 10)
```
Patient 1 had an event at time 434 days, patient 2 had an event at time 86 days, patient 3 was censored at time 161 days, etc.

```{r}
## Compute survival curve with Kaplan-Meier method
s1 <- survfit(Surv(Time , Status) ~ 1, data = df_annotation_part_1_final)
str(s1)
```
Some key components of this object that will be used to create survival curves include:
- time: the timepoints at which the curve has a step, i.e. at least one event occurred.
- surv: the estimate of survival at the corresponding time.

```{r}
## Kaplan-Meier plots
survfit2(Surv(Time, Status) ~ 1, data = df_annotation_part_1_final) %>% 
  ggsurvfit(lwd = 1) +
  labs(x = "Days", y = "Overall Survival Probability",
       title = "Survival Plot") + ## basic plot
  add_confidence_interval() + ## confidence interval
  add_risktable()           + ## numbers at risk
  theme_gray() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
```


One quantity of interest in a survival analysis is the probability of surviving beyond a certain number of years x. For example, to estimate the probability of surviving to 1 year, use summary function with the times argument. The variable Time is in days and we need to use time = 365.25
```{r}
## Estimating x-year survival
fit <- survfit(Surv(Time, Status) ~ 1,
               data = df_annotation_part_1_final)
summary_fit <- summary(fit, times = 365.25)
summary_fit
```
We find that the 1-year probability of survival in this study is 67.3%. The associated lower an upper bounds are of the 95% confidence interval are: 62.5% and 72.5%. The 1-year survival probability is the point on the y-axis that corresponds to 1 year on the x-axis for the survival curve.

```{r}
## Create df
my_times <- c(365)
df       <- data.frame(times = my_times,
                       probs = summary_fit$surv) 

## Let's see the 1-year probability
survfit2(Surv(Time, Status) ~ 1, data = df_annotation_part_1_final) %>% 
  ggsurvfit(lwd = 1) +
  labs(x = "Days", y = "Overall Survival Probability",
       title = "Survival Plot") + ## basic plot
  add_confidence_interval() + ## confidence interval
  add_risktable()           + ## numbers at risk
  geom_segment(data = df,
               aes(x = my_times, y = 0, xend = times, yend = probs),
               linetype = "dashed", color = "red", lwd = 1)+ 
  geom_segment(data = df,
               aes(x = 0, y = probs, xend = times, yend = probs),
               linetype = "dashed", color = "red", lwd = 1) +
  theme_gray() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
```

What happens if you use a “naive” estimate? Here “naive” means that the patients who were censored prior to 1-year are considered event-free and included in the denominator.

121 of the 228 patients in the lung data died by 1
 year so the “naive” estimate is calculated as:

$(1−\frac{121}{228})\cdot100 = 47\%$

You get an incorrect estimate of the 1
-year probability of survival when you ignore the fact that 42 patients were censored before 1
 year.

Recall the correct estimate of the 1
-year probability of survival, accounting for censoring using the Kaplan-Meier method, was 41%.

Ignoring censoring leads to an overestimate of the overall survival probability. Imagine two studies, each with 228 subjects. There are 165 deaths in each study. Censoring is ignored in one (blue line), censoring is accounted for in the other (yellow line). The censored subjects only contribute information for a portion of the follow-up time, and then fall out of the risk set, thus pulling down the cumulative probability of survival. Ignoring censoring erroneously treats patients who are censored as part of the risk set for the entire follow-up period.


```{r}
## x-time survival probability estimate
survfit(Surv(Time, Status) ~ 1, data = df_annotation_part_1_final) %>% 
  tbl_survfit(
    times = 365.25,
    label_header = "**1-year survival (95% CI)**")
```

Another quantity of interest in a survival analysis is the average time, which we quantify using the median. Survival times are not expected to be normally distributed so the mean is not an appropriate summary.
```{r}
## Estimating median survival time
fit
```
The median survival time is 640 days. The lower and upper bounds of the 95% confidence interval are: 547 days and 777 days.
Median survival is the time corresponding to a survival probability of 0.5

```{r}
## Create df
my_times <- c(636)
df       <- data.frame(times = my_times,
                       probs = 0.5) 

## Let's see the 1-year probability
survfit2(Surv(Time, Status) ~ 1, data = df_annotation_part_1_final) %>% 
  ggsurvfit(lwd = 1) +
  labs(x = "Days", y = "Overall Survival Probability",
       title = "Survival Plot") + ## basic plot
  add_confidence_interval() + ## confidence interval
  add_risktable()           + ## numbers at risk
  geom_segment(data = df,
               aes(x = my_times, y = 0, xend = times, yend = probs),
               linetype = "dashed", color = "red", lwd = 1)+ 
  geom_segment(data = df,
               aes(x = 0, y = probs, xend = times, yend = probs),
               linetype = "dashed", color = "red", lwd = 1) +
  theme_gray() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
```

What happens if we yse a "naive" estimate? Here "naive" means that we exclude the censored patients from the calculation entirely to estimate median survival time among the patients who have had the event.
Summarize the median survival time among the patients who died.
```{r}
## Compute
df_annotation_part_1_final %>% 
  filter(Status == 1) %>% 
  summarize(median_surv = median(Time))
```
We get an incorrect estimate of median survival time of 570 days when we ignore the fact that the censored patients also contribute follow-up time. The correct estimate of median survival time is 636 days.

Ignoring censoring will lead to an underestimate of median survival time because the follow-up time that censored patients contribute is excluded (blue line). The true survival curve accounting for censoring is the yellow one.
```{r}
## Median survival time
survfit(Surv(Time, Status) ~ 1, data = df_annotation_part_1_final) %>% 
  tbl_survfit(
    probs = 0.5,
    label_header = "**Median survival (95% CI)**")
```


We can conduct between-group significance tests using a log-rank test. The log-rank test equally weights observations over the entire follow-up time and is the most common way to compare survival times between groups.
```{r}
## Difference wrt Sex
fit_sex <- survdiff(Surv(Time, Status) ~ Sex,
                    data = df_annotation_part_1_final)

## Plot
survfit2(Surv(Time, Status) ~ Sex,
         data = df_annotation_part_1_final) %>% 
  ggsurvfit(lwd = 1) +
  labs(x = "Days", y = "Overall Survival Probability",
       title = "Survival Plot") + ## basic plot
  add_confidence_interval() + ## confidence interval
  add_risktable()           + ## numbers at risk
  add_legend_title("Sex") +
  theme_gray() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
```

We see that there was not a significant difference in overall survival according to sex in this study, with a p-value of p = 0.5

```{r}
## Difference wrt Response or Not
fit_response <- survdiff(Surv(Time, Status) ~ Response,
                         data = df_annotation_part_1_final)

## Plot
survfit2(Surv(Time, Status) ~ Response,
         data = df_annotation_part_1_final) %>% 
  ggsurvfit(lwd = 1) +
  labs(x = "Days", y = "Overall Survival Probability",
       title = "Survival Plot") + ## basic plot
  add_confidence_interval() + ## confidence interval
  add_risktable()           + ## numbers at risk
  add_legend_title("Response") +
  theme_gray() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
```

We see that there was a significant difference in overall survival according to response of immunotherapy in this study,
with a p-value of p <2e-16.

We can obtain tables of results with the option to return the hazard ration rather than the log hazard ratio.
```{r}
## Compute
coxph(Surv(Time, Status) ~ Sex,
      data = df_annotation_part_1_final) %>% 
  tbl_regression(exp = TRUE) 
```

The quantity of interest from a Cox regression model is a hazard ratio (HR). The HR represents the ratio of hazards between two groups at any particular point in time. The HR is interpreted as the instantaneous rate of occurrence of the event of interest in those who are still at risk for the event. It is not a risk, through it is commonly mis-interpreted as such. A HR < 1, indicated reduced hazard of death whereas a HR > 1 indicates an increased hazard of death.
So the HR of 0.91 implies that 0.91 times as many females are dying as males, at any given time. Stated differently, females have a significantly lower hazard of death than males in these data.

### Part 2 - Landmark Analysis and Time Dependent Covariates
In Part 1 we covered using log-rank tests and Cox regression to examine associations between covariates of interest and survival outcomes. But these analyses rely on the covariate being measured at baseline, that is, before follow-up time for the event begins. What happens if you are interested in a covariate that is measured after follow-up time begins?

Example: Overall survival is measured from treatment start, and interest is in the association between complete response to treatment and survival.

Anderson et al (JCO, 1983) described why traditional methods such as log-rank tests or Cox regression are biased in favor of responders in this scenario, and proposed the landmark approach. The null hypothesis in the landmark approach is that survival from landmark does not depend on response status at landmark.

Some other possible covariates of interest in cancer research that may not be measured at baseline include:

- transplant failure
- graft versus host disease
- second resection
- adjuvant therapy
- compliance
- adverse events

Variables of interest include:
1. time_01: Observed survival times in days
2. time_02: Progression-free survival (PFS) times in days
2. status: censoring status 1 = censored, 2 = dead
3. sex: 1 = Male, 2 = Female
4. response: 1 = Partial Response, 2 = Complete Response,
             3 = Stable Disease, 4 = Progression Disease
5. stage: stage of the disease

```{r}
## Check
colnames(df_annotation_part_1)
```

Approach:
1. Select a fixed time after baseline as your landmark time. Note: this should be done based on clinical information, prior to data inspection

2. Subset population for those followed at least until landmark time. Note: always report the number excluded due to the event of interest or censoring prior to the landmark time.

3. Calculate follow-up from landmark time and apply traditional log-rank tests or Cox regression.

1. Landmark Time
[Reference](https://jamanetwork.com/journals/jamaoncology/fullarticle/2805798) ---> Landmark Time: 1 year

2. Subset population for those followed at least until landmark time
```{r}
## Subset
df_annotation_part_2 <- 
  df_annotation_part_1 %>% 
  filter(Time >= 365*2) 

message("Initial Patients: ")
dim(df_annotation_part_1)[1]
message("\n")

message("Current Patients: ")
dim(df_annotation_part_2)[1]
message("\n")

message("Patients Excluded: ")
dim(df_annotation_part_1)[1]-dim(df_annotation_part_2)[1]
```

3. Calculate follow-up time from landmark and apply traditional methods.
```{r}
## Compute
df_annotation_part_2 <- 
  df_annotation_part_2 %>% 
  mutate(LM_Time = Time - 365*2)
```

```{r}
## Plot
survfit2(Surv(LM_Time, Status) ~ Initial_Stage,
         data = df_annotation_part_2) %>% 
  ggsurvfit(lwd = 1) +
  labs(
    x = "Days from 2-years landmark",
    y = "Overall survival probability", title = "Survival Plot") +
  add_risktable() +
  add_legend_title("Tumor Stage") +
  theme_gray() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
```


### Part 3 - Competing Risks
Competing risks analyses may be used when subjects have multiple possible events in a time-to-event setting.

Examples:

- recurrence
- death from disease
- death from other causes
- treatment response
All or some of these (among others) may be possible events in any given study. The fundamental problem that may lead to the need for specialized statistical methods is unobserved dependence among the various event times. For example, one can imagine that patients who recur are more likely to die, and therefore times to recurrence and times to death would not be independent events.

There are two approaches to analysis in the presence of multiple potential outcomes:

- Cause-specific hazard of a given event: this represents the rate per unit of time of the event among those not having failed from other events

- Subdistribution hazard of a given event: this represents the rate per unit of time of the event as well as the influence of competing events
Each of these approaches may only illuminate one important aspect of the data while possibly obscuring others, and the chosen approach should depend on the question of interest.

When the events are independent (almost never true), cause-specific hazards is unbiased. When the events are dependent, a variety of results can be obtained depending on the setting. Cumulative incidence using 1 minus the Kaplan-Meier estimate is always >= cumulative incidence using competing risks methods, so can only lead to an overestimate of the cumulative incidence, though the amount of overestimation depends on event rates and dependence among events.
To establish that a covariate is indeed acting on the event of interest, cause-specific hazards may be preferred for treatment or prognostic marker effect testing. To establish overall benefit, subdistribution hazards may be preferred for building prognostic nomograms or considering health economic effects to get a better sense of the influence of treatment and other covariates on an absolute scale.

```{r}
## Check data
colnames(df_annotation_part_2)
```
```{r}
## Format data
df_annotation_part_3 <- df_annotation_part_2

## Age
df_annotation_part_3$Age <- as.integer(df_annotation_part_2$Patient_Age_at_Diagnosis)

## Histology Harmomnized
df_annotation_part_3 <- df_annotation_part_3 %>% 
  mutate(Tumor_Type = case_when(
    Histology_Harmonized == "Adeno" ~ 1,
    Histology_Harmonized == "LC-NE" ~ 2,
    Histology_Harmonized == "Squamous" ~ 3,
    TRUE ~ 4))

## Agent PD1 Category
df_annotation_part_3 <- df_annotation_part_3 %>% 
  mutate(Agent_PD1 = case_when(
    Agent_PD1_Category == "PD(L)1" ~ 1,
    Agent_PD1_Category == "PD(L)1 + CTLA4" ~ 2,
    TRUE ~ 4))
```

```{r}
## Check
str(df_annotation_part_3)
```

Cumulative Incidence for competing risks
```{r}
## Compute
cuminc(Surv(Time, factor(Status)) ~ 1, data = df_annotation_part_3)
```

```{r}
## Plot Cumulative Incidence
cuminc(Surv(Time, factor(Status)) ~ 1, data = df_annotation_part_3) %>% 
  ggcuminc(lwd = 1) + 
  labs(x = "Days") + 
  add_confidence_interval() +
  add_risktable()
```

```{r}
## Incidence of disease wrt sex
cuminc(Surv(Time, factor(Status)) ~ Sex,
            data = df_annotation_part_3) %>% 
  tbl_cuminc(times = 1826.25, 
    label_header = "**{time/365.25}-year cuminc**") %>% 
  add_p()

## Smoking Status
cuminc(Surv(Time, factor(Status)) ~ Patient_Smoking_Status,
            data = df_annotation_part_3) %>% 
  tbl_cuminc(times = 1826.25, 
    label_header = "**{time/365.25}-year cuminc**") %>% 
  add_p()

## Line of Therapy
cuminc(Surv(Time, factor(Status)) ~ Line_of_Therapy,
            data = df_annotation_part_3) %>% 
  tbl_cuminc(times = 1826.25, 
    label_header = "**{time/365.25}-year cuminc**") %>% 
  add_p()

## Age
cuminc(Surv(Time, factor(Status)) ~ Age,
            data = df_annotation_part_3) %>% 
  tbl_cuminc(times = 1826.25, 
    label_header = "**{time/365.25}-year cuminc**") %>% 
  add_p()

## Patient Race Type
cuminc(Surv(Time, factor(Status)) ~ Patient_Race,
            data = df_annotation_part_3) %>% 
  tbl_cuminc(times = 1826.25, 
    label_header = "**{time/365.25}-year cuminc**") %>% 
  add_p()
```

```{r}
## Plots

## Sex
cuminc(Surv(Time, factor(Status)) ~ Sex,
       data = df_annotation_part_3) %>% 
  ggcuminc() + 
  labs(x = "Days") + 
  add_confidence_interval() +
  add_risktable() +
  add_legend_title("Sex") +
  theme_gray() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

## Initial Stage
cuminc(Surv(Time, factor(Status)) ~ Initial_Stage,
       data = df_annotation_part_3) %>% 
  ggcuminc() + 
  labs(x = "Days") + 
  add_confidence_interval() +
  add_risktable() +
  add_legend_title("Initial Stage") +
  theme_gray() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

## Line of Therapy
cuminc(Surv(Time, factor(Status)) ~ Line_of_Therapy,
       data = df_annotation_part_3) %>% 
  ggcuminc() + 
  labs(x = "Days") + 
  add_confidence_interval() +
  add_risktable() +
  add_legend_title("Line of Therapy") +
  theme_gray() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

## Response
cuminc(Surv(Time, factor(Status)) ~ Response,
       data = df_annotation_part_3) %>% 
  ggcuminc(lwd = 1) + 
  labs(x = "Days") + 
  add_risktable() +
  add_legend_title("Response") +
  theme_gray() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
```

Competiting Risk Regression
```{r}
## Model
crr(Surv(Time, factor(Status)) ~ Sex + Age + Response + Initial_Stage +
      Patient_Smoking_Status + Line_of_Therapy + Agent_PD1 +
      Patient_Race + Tumor_Type, data = df_annotation_part_3)
```
```{r}
## Check
crr(Surv(Time, factor(Status)) ~ Sex + Age + Response + Initial_Stage +
      Patient_Smoking_Status + Line_of_Therapy + Agent_PD1 +
      Patient_Race + Tumor_Type, data = df_annotation_part_3) %>% 
  tbl_regression(exp = TRUE)
```

Relevant factors:
- Age, Response, Patient Smoking Status, Line of therapy, Agent PD1, Patient Race.

### Part 4 - Advanced Topics
In this section I’ll include a variety of bits and pieces of things that may come up and be handy to know:

- Assessing the proportional hazards assumption
- Making a smooth survival plot based on x-year survival according to a continuous covariate
- Conditional survival

```{r}
## Collect data
df_annotation_part_4 <- df_annotation_part_3 
```

Assessing proportional hazards
```{r}
## Cox proportional hazards regression model
mv_fit <- coxph(Surv(Time, Status) ~ Sex + Age + Response +
                       Initial_Stage + Patient_Smoking_Status +
                       Line_of_Therapy + Agent_PD1 +
                       Patient_Race + Tumor_Type,
                     data = df_annotation_part_4)
```

```{r}
## Analysis
mv_fit
```

```{r}
## Summary
summary(mv_fit)
```

```{r}
## Analysis
cz     <- cox.zph(mv_fit)
print(cz)
```

```{r}
## Plot
ggcoxzph(cz)
```

Here we see that with p-values > 0.05, we do not reject the null hypothesis, and conclude that the proportional hazards assumption is satisfied for each individual covariate, and also for the model overall.

Smooth Survival Plot
```{r}
## Smooth Survival
sm.options(list(xlab = "Age (Years)",
                ylab = "Median time to death (Years)"))

## Format Age
df_annotation_part_4$Age <- na.aggregate(df_annotation_part_4$Age,
                                         FUN = median)

## Plot
ggcoxdiagnostics(mv_fit, type = "schoenfeld",
                 hline.size = 1.2,
                 sline.size = 1.2,
                 title = "Residual Plot",
                 subtitle = "using Scaled Schoenfeld") +
  geom_smooth()
```

- The x's represent events
- The o's represent censoring
- The line is a smoothed estimate of median survival according to age. (In this case too smooth)

The option h is the smoothing parameter. This should be related to the standard deviation of the continuous covariate, x. Suggested to start eith $\frac{sd(x)}{n^\frac{-1}{4}}$ then reduce by $\frac{1}{2}$, $\frac{1}{4}$, etc. to get a good amount of smoothing. The previous plot was too smooth so let's reduce it by $\frac{1}{6}$.
```{r}
## Plot
ggcoxdiagnostics(mv_fit, type = "deviance",
                 hline.size = 1.5,
                 sline.size = 1.5,
                 point.size = 2,
                 title = "Deviance Plot",
                 linear.predictions = FALSE, ggtheme = theme_bw())
```

Now we can see that the median time to death increase slightly as age is between 55 and 65, and increase slightly again when age is above 78.


Conditional Survival
Sometimes it is of interest to generate survival estimates among a group of patients who have already survived for some length of time.
$$S(y|x) = \frac{S(x + y)}{S(x)}$$
- y: number of additional survival years of interest
- x: number of years a patient has already survived

Let's condition on survival to 6-months.
```{r}
## Fit
fit_cond <- survfit(Surv(Time, Status) ~ 1,
                     data = na.omit(df_annotation_part_4))
```

```{r}
## Condition on survival to 6-months
prob_times <- c(365.25)
```

```{r}
## Plot
purrr::map_df(prob_times, ~conditional_surv_est(basekm = fit_cond,
                                                t1 = prob_times,
                                                t2 = .x)) %>% 
  mutate(months = round(prob_times / 30.4)) %>% 
  select(months, everything())
```

```{r}
## Plot
gg_conditional_surv(basekm = fit_cond, at = prob_times,
                    main = "Conditional survival in NSCLC data",
                    xlab = "Days") +
  labs(color = "Time")
```


