---
title: "Similarity Network Fusion (SNF) - DEGs Genes, All Data"
author: "Davide Mascolo"
date: "2023-09-06"
output: html_document
---

## Utils

```{r setup, include = FALSE}
library(tidyverse)
library(SNFtool)
library(e1071)
library(ggplot2)
library(readxl)
library(flexclust)
library(glue)
library(igraph)
library(gplots)
library(caret)
library(stats)
library(ggsurvfit)
library(survival)
```

## Custom Functions

```{r}
## Create a function that returns the string in correct form
clean_patient <- function(patients_list){
  ## Input: list of patients code to format
  ## Output: code formatted
  return(gsub("\\.", "-", patients_list))
}

optimal_cluster <- function(affinity_matrix, C, label){
  ## Create an empty lists to save NMI values
  NMI_values     <- list()
  ## Define an empty dataframe where to collect the final result
  df_cluster <- data.frame(K = c(C),
                           NMI = rep(0, length(C))) 
  ## Compute clustering
  for (i in C){
    cluster    <- spectralClustering(affinity_matrix, K = i)
    ## Plot
    displayClustersWithHeatmap(affinity_matrix, cluster,
                               main = glue("Clustering with K = {i}"))
    NMI_values <- append(NMI_values, calNMI(cluster, label))}
  df_cluster$NMI <- NMI_values
  return(df_cluster)
}

## Use a function to test enrichment clusters
enrichment <- function(x, m, n, k, alpha){
if (phyper(x[[1]], m[[1]], n[[1]], k[[1]], lower.tail = F) <= alpha){
  print("Significant Enrichment")
} else{
  print("Not Significant Enrichment")
}}
```

## Load Data

```{r}
## Set path
path <- getwd()

## Load Data

## Rna Gene Counts 
df_rna_counts <- read.csv(paste0(path, "/Data/rna_counts.csv"))

## Exome  
df_wes <- read.csv(paste0(path, "/Data/Exome_Genes.csv"))

## Load DEGs genes
df_degs <- read.csv(paste0(path, "/Data/diff_expressed_genes.csv"))
df_degs <- df_degs$hgnc_symbol

## Load 10% Differential Co-Expressed
df_10_hubs <- c("GAS7", "ANO2", "EYA2", "MOV10L1", "ADCYAP1R1",
                "AURKA", "EBF4", "GZMH", "SYNDIG1", "MEOX2",
                "CDH23", "HLF", "GPRC5D", "PCDHB6", "CCN2",
                "PCDHB10", "PCDHB12", "TMEM156", "MOCS1", "KCNK17",
                "KLRD1", "ADGRB3", "SMAD6", "FRAS1", "PTPRQ", "ARMH4",
                "CDH13", "ASXL3", "CCN1", "FLG2", "FLG", "NT5DC4",
                "LRTM1", "SHC3", "HMCN2", "FAM13C", "GGTLC1", "HSPB8",
                "TCF7L1", "C4orf19", "EPHB1", "C2CD6", "AFF2",
                "H2BC5", "LRRC36", "CILP2", "CD3G", "CADPS", "SPRY1",
                "C8orf48", "RET", "TUB", "SLC26A5", "ID4", "SYNPO2",
                "BNC2", "ADCY5", "NPAS4", "SLC66A1L", "LPL", "ZNF683",
                "PCDHB9", "TIGIT", "IZUMO1", "KCNB2", "FAM110C",
                "ROBO2", "PBX1", "RTN4RL1", "MAGI2", "RELN", "H2BC26",
                "DACT3", "DCHS2", "MT1F", "GRIN3A", "GJC2", "PKHD1L1",
                "MT1H", "C2CD4B", "DOK6", "PLXNA4", "UPK3B", "PTCHD4",
                "FAM72C", "FXYD1", "H2BC8", "H2AC14", "H2BC7")

## Clinical
df_clinical <- read_excel(paste0(path, "/Data/SU2C-MARK_Supplementary_Tables_Combined_v5_Filtered.xlsx"),
                         sheet = "Table_S1_Clinical_Annotations",
                         skip = 2)

## Immune Signatures
df_immune <- read_excel(paste0(path, "/Data/SU2C-MARK_Supplementary_Tables_Combined_v5_Filtered.xlsx"),
                         sheet = "Table_S18_Immune_Signatures")

## Myeloid Signatures
df_myeloid <- read_excel(paste0(path, "/Data/SU2C-MARK_Supplementary_Tables_Combined_v5_Filtered.xlsx"),
                         sheet = "Table_S19_Myeloid_Signatures")

## Curated Signatures
df_curated <- read_excel(paste0(path, "/Data/SU2C-MARK_Supplementary_Tables_Combined_v5_Filtered.xlsx"),
                         sheet = "Table_S20_Curated_Signatures")


## Some pre-processing

## Rna Gene Counts
df_rna_counts$Name        <- NULL
gene_names                <- df_rna_counts$Description
df_rna_counts$Description <- NULL
colnames(df_rna_counts)   <- clean_patient(colnames(df_rna_counts))
df_rna_counts             <- data.frame(t(df_rna_counts))
colnames(df_rna_counts)   <- gene_names

## Exome
wes_patients     <- df_wes$Tumor_Sample_Barcode
rownames(df_wes) <- clean_patient(wes_patients)
df_wes           <- df_wes[,-2]
df_wes$X         <- NULL

## Clinical data
df_clinical$Harmonized_SU2C_Participant_ID_v2 <- paste(
  df_clinical$Harmonized_SU2C_Participant_ID_v2, "T1", sep = "-")

## Immune
immune_patients <- df_immune$Harmonized_SU2C_RNA_Tumor_Sample_ID_v2
df_immune$Harmonized_SU2C_RNA_Tumor_Sample_ID_v2 <- NULL
rownames(df_immune) <- immune_patients

## Myeloid
myeloid_patients <- df_myeloid$Harmonized_SU2C_RNA_Tumor_Sample_ID_v2
df_myeloid$Harmonized_SU2C_RNA_Tumor_Sample_ID_v2 <- NULL
rownames(df_myeloid) <- myeloid_patients

## Curated
curated_patients <- df_curated$Harmonized_SU2C_RNA_Tumor_Sample_ID_v2
df_curated$Harmonized_SU2C_RNA_Tumor_Sample_ID_v2 <- NULL
rownames(df_curated) <- curated_patients
```

## Data Wrangling

```{r}
## Check
dim(df_rna_counts);dim(df_wes);dim(df_immune);dim(df_myeloid);dim(df_curated)
```

```{r}
## At this point, is possible to filter the patients of WES data using the patients that are in RNA-Seq data.

## Number of patients in common: 65
common_patients <- Reduce(intersect, list(rownames(df_rna_counts),
                                          rownames(df_wes),
                                          rownames(df_curated),
                                          rownames(df_myeloid),
                                          rownames(df_curated)))
                             

## Filter the dataframe with two different sets of patients
## Rna Counts
df_rna_counts_final <- df_rna_counts[rownames(df_rna_counts) %in%
                                       common_patients,
                                     colnames(df_rna_counts) %in%
                                       df_10_hubs]
dim(df_rna_counts_final)
## Dim: 65 patients x 57523 genes

## Wes
df_wes_final        <- df_wes[rownames(df_wes)
                              %in% common_patients,
                              colnames(df_wes) %in%
                                df_10_hubs]
dim(df_wes_final)
## Dim: 65 patients x 16270 genes

## Immune
df_immune_final     <- df_immune[rownames(df_immune)
                                 %in% common_patients, ]
dim(df_immune_final);View(df_immune_final)

## Myeloid
df_myeloid_final        <- df_myeloid[rownames(df_myeloid)
                              %in% common_patients,]
dim(df_myeloid_final);View(df_myeloid_final)

## Curated
df_curated_final        <- df_curated[rownames(df_curated)
                              %in% common_patients,]
dim(df_curated_final);View(df_curated_final)

## Extract true label
## RNA
df_clinical_filter <- df_clinical %>% 
  select(Harmonized_SU2C_Participant_ID_v2,
         Harmonized_Confirmed_BOR,
         Patient_Age_at_Diagnosis, Patient_Sex,
         Harmonized_PFS_Event, Harmonized_PFS_Days,
         Harmonized_OS_Event, Harmonized_OS_Days,
         Harmonized_Confirmed_BOR, Initial_Stage,
         Patient_Race, Patient_Smoking_Status,
         Histology_Harmonized, Line_of_Therapy,
         Agent_PD1_Category,
         Patient_Smoking_Status) %>% 
  filter(Harmonized_SU2C_Participant_ID_v2 %in% common_patients)
true_label <- df_clinical_filter$Harmonized_Confirmed_BOR
true_label_smoking <- df_clinical_filter$Patient_Smoking_Status 

## Format
true_label <- case_when(true_label == "PR" ~ 1,
                        true_label == "PD" ~ 2,
                        true_label == "SD" ~ 2,
                        TRUE ~ 1)
```

```{r}
## Check
dim(df_rna_counts_final);dim(df_wes_final);dim(df_immune_final);dim(df_curated_final);dim(df_myeloid_final)
```

## SNF

### Compute distances

In this chunk is possible to compute matrices for both datasets. Here we use the default euclidean distance for RNA-Seq data and the hamming distance for WES data.

```{r}
## Scaling
## RNA-Seq
df_rna_counts_scaled <- standardNormalization(df_rna_counts_final)
## Immune
df_immune_scaled     <- standardNormalization(df_immune_final)
## Curated
df_curated_scaled    <- standardNormalization(df_curated_final)
## Myeloid
df_myeloid_scaled    <- standardNormalization(df_myeloid_final)
## WES
df_wes_scaled        <- df_wes_final  

## Compute distances
## RNA-Seq
dist_rna_counts     <- (dist2(as.matrix(df_rna_counts_scaled),
                           as.matrix(df_rna_counts_scaled)))^(1/2)
## Immune
dist_immune  <- (dist2(as.matrix(df_immune_scaled),
                           as.matrix(df_immune_scaled)))^(1/2)
## Curated
dist_curated <- (dist2(as.matrix(df_curated_scaled),
                           as.matrix(df_curated_scaled)))^(1/2)
## Myeloid
dist_myeloid <- (dist2(as.matrix(df_myeloid_scaled),
                           as.matrix(df_myeloid_scaled)))^(1/2)
## WES
dist_wes            <- (dist2(as.matrix(df_wes_scaled),
                              as.matrix(df_wes_scaled),
                              method = "binary"))^(1/2)
```

```{r}
## Check
dim(dist_rna_counts)[1] == dim(df_rna_counts_scaled)[1]
dim(dist_immune)[1] == dim(df_immune_scaled)[1]
dim(dist_curated)[1] == dim(df_curated_scaled)[1]
dim(dist_myeloid)[1] == dim(df_myeloid_scaled)[1]
dim(dist_wes)[1]        == dim(df_wes_scaled)[1]
```

### Affinity Matrix

To convert distance matricies to similarity matricies, is possible to use affinityMatrix, which takes three arguments: - distance matrix - k: the number of neighbours, where affinities outsied of the neighbourhouud are set to zero (10\~30) - sigma: is the hyperparameter for the scaled exponential similarity kernel used to conduct the acual affinity calculation. Both of these parameters are chosen empirically. (0.3\~0.8) - T: number of iterations. (10\~30)

```{r}
## Parameters
C <- 2
K <- 15
t <- 30
alpha <- 0.8
```

```{r}
## Affinity Matrix
W_1 <- affinityMatrix(dist_rna_counts, K = K, sigma = alpha)
W_2 <- affinityMatrix(dist_immune, K = K, sigma = alpha)
W_3 <- affinityMatrix(dist_curated, K = K, sigma = alpha)
W_4 <- affinityMatrix(dist_myeloid, K = K, sigma = alpha)
W_5 <- affinityMatrix(dist_wes, K = K, sigma = alpha)
```

### Spectral Clustering
```{r}
## Clustering
cluster_rna_counts <- optimal_cluster(W_1, C, true_label)
cluster_immune     <- optimal_cluster(W_2, C, true_label)
cluster_curated    <- optimal_cluster(W_3, C, true_label)
cluster_myeloid    <- optimal_cluster(W_4, C, true_label)
cluster_wes        <- optimal_cluster(W_5, C, true_label)

## Spectral Clustering
cluster_rna_counts_final <- spectralClustering(W_1, K = C)
cluster_immune_final     <- spectralClustering(W_2, K = C)
cluster_curated_final    <- spectralClustering(W_3, K = C)
cluster_myeloid_final    <- spectralClustering(W_4, K = C)
cluster_wes_final        <- spectralClustering(W_5, K = C)
```

```{r}
## Save the patients for each community
## RNA-Seq
communities_rna <- data.frame(ID_Patient = c(common_patients),
                  Community = c(cluster_rna_counts_final),
                  Response = c(true_label),
                  Sex = df_clinical_filter$Patient_Sex,
                  Time = df_clinical_filter$Harmonized_OS_Days,
    Smoking_Status = df_clinical_filter$Patient_Smoking_Status)
## WES
communities_wes <- data.frame(ID_Patient = c(common_patients),
                   Community = c(cluster_wes_final),
                   Response = c(true_label),
                   Sex = df_clinical_filter$Patient_Sex,
                   Time = df_clinical_filter$Harmonized_OS_Days,
    Smoking_Status = df_clinical_filter$Patient_Smoking_Status)
```

### Fusion Network

It's possible to see both matricies have some information about clusters in them.

```{r}
## Fusion algorithm
W <- SNF(list(W_1, W_2, W_3, W_4, W_5), t, t)

## Clustering with best C <- 3
final_clusters <- spectralClustering(W, K = C)

## Plot
displayClustersWithHeatmap(W,
              spectralClustering(W, K = C)) ## To analyze using clinical features (EDA)

## Evaluate
calNMI(final_clusters, true_label)
```

It's also possible to find the concordance between each individual network and the fused network

```{r}
## Concordance Matrix
(concordance_matrix      <- concordanceNetworkNMI(list
                                (W, W_1, W_2, W_3, W_4, W_5), C))
## This output shows the concordance between the fused network and each individual network.
```

How many patients Response/Non-Response are in the different clusters?

```{r}
## Save the patients for each community
communities <- data.frame(ID_Patient = c(common_patients),
                          Community = c(final_clusters),
                          Response = c(true_label),
                  Sex = df_clinical_filter$Patient_Sex,
                  Time = df_clinical_filter$Harmonized_OS_Days,
        Smoking_Status = df_clinical_filter$Patient_Smoking_Status)
## Remember: True_Label = 1 --> Response
##           True_Label = 2 --> Resistance

## Check
dim(communities)
```

## Plot

```{r}
## Community
ggplot(communities, aes(x = Community, y = after_stat(count))) +
  geom_bar(color = "steelblue", fill = "steelblue") +
  ggtitle(label = "Clusters Distribution",
          subtitle = "for Similarity Network Fusion") +
  ylab("N.") +
  theme_grey()
```

We can conduct between-group significance tests using a log-rank test. The log-rank test equally weights observations over the entire follow-up time and is the most common way to compare survival times between groups.

```{r}
## Create dataframe for median probability


## Difference wrt Community
model_fit <- survdiff(Surv(Time, Response) ~ Community,
                      data = communities)

## Plot
survfit2(Surv(Time, Response) ~ Community,
         data = communities) %>% 
  ggsurvfit(lwd = 1.3) +
  labs(x = "Days", y = "Overall Survival Probability",
       title = "Survival Plot") + ## basic plot
  add_risktable()           + ## numbers at risk
  add_legend_title("Community") +
  theme_gray() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

## Check
model_fit
```

The following hypotheses are used in this test:

$H_0$: There is no difference in survival between the groups.

$H_1$: There is a difference in survival between the groups.

With one degree of freedom, the Chi-Squared test statistic is 7.8, and the associated p-value is 0.005. We REJECT the null hypothesis because the p-value is smaller than 0.05 and also 0.01.

```{r}
## Check

## Response
communities %>% 
  filter(Community == 1) %>% 
  summarize(median_surv = median(na.omit(Time)))

## Resistance
communities %>% 
  filter(Community == 2) %>% 
  summarize(median_surv = median(na.omit(Time)))
```

The median survival time is:
- 214 days for patients who are in Community 1
- 470 days for patients who are in Community 2.

## Enrichment Clusters Analysis (Hypergeometric Distribution)
```{r}
## Patients who are Response in different communities

## Response
resp_snf_comm_01 <- communities %>%
  filter(Response == 1 & Community == 1) %>% 
  count()
resp_snf_comm_02 <- communities %>%
  filter(Response == 1 & Community == 2) %>% 
  count()
## Resistance
non_resp_snf_comm_01 <- communities %>%
  filter(Response == 2 & Community == 1) %>% 
  count()
non_resp_snf_comm_02 <- communities %>%
  filter(Response == 2 & Community == 2) %>% 
  count()

## Number of patients for each community
n_comm_01_snf <- communities %>%
  filter(Community == 1) %>% 
  count()
n_comm_02_snf <- communities %>%
  filter(Community == 2) %>% 
  count()

## Successes in population
succ_pop     <- length(true_label[true_label == 1])
## Non-Successes in population
non_succ_pop <- length(true_label[true_label == 2])
```

```{r}
## How to use the function:
## phyper(x/q, m, n, k)
## x: number of successes in the samples
## m: number of successes in the population
## n: number of failures in the population
## k: size of the sample or the number of trials

## Probabilità di ottenere X o meno pazienti, con risposta all'immunoterapia sul totale della popolazione considerata.


## Hypergeometric Distribution
## lower.tail = F ---> P[X > x] (Scelta Effettuata)
## lower.tail = T ---> P[X <= x] (Default)

print("SNF Clusters:")
## Community 01 - Response
print("Community 01 Response:")
enrichment(resp_snf_comm_01, succ_pop,
       non_succ_pop, n_comm_01_snf, alpha = 0.05)
## Community 02 - Response
print("Community 02 Response:")
enrichment(resp_snf_comm_02, succ_pop,
           non_succ_pop, n_comm_02_snf,  alpha = 0.05)
## Significativo
## We can reject the null hypothesis and assume a significant enrichment, that is, there is a small probablity of seing an equal or bigger overlap than x.

## Community 01 - Resistance (for resitance group, is important to consider the success such as non success)
print("Community 01 Resistance:")
enrichment(non_resp_snf_comm_01, non_succ_pop,
           succ_pop, n_comm_01_snf, alpha = 0.05)
## Significativo
## We can reject the null hypothesis and assume a significant enrichment, that is, there is a small probablity of seing an equal or bigger overlap than x.
## Community 02 - Resitance
print("Community 02 Resistance:")
enrichment(non_resp_snf_comm_02, non_succ_pop,
           succ_pop, n_comm_02_snf, alpha = 0.05)
```


```{r}
## For each cluster save the list of patients
## Community 01
community_01 <- communities %>% 
  filter(Community == 1)
## Community 02
community_02 <- communities %>% 
  filter(Community == 2)

## Save
write.csv(community_01, paste0(path, "/Clusters/community_01.csv"),
          row.names = F)
write.csv(community_02, paste0(path, "/Clusters/community_02.csv"),
          row.names = F)
```

Use label propagation to predict the labels of new data points.
```{r}
## Predictions

## Create training and test data
n            <- floor(0.6 * length(true_label)) ## training samples
train_sample <- sample.int(length(true_label), n) 
x_train      <- lapply(W, function(x) W[train_sample, ])
x_test       <- lapply(W, function(x) W[-train_sample, ])
groups       <- true_label[train_sample]
```

```{r}
## Parameters
K      <- 15
alpha  <- 0.8
t      <- 30
method <- T
```

```{r}
## Apply prediction
y_pred <- groupPredict(x_train, x_test, groups, K, alpha, method)
```

```{r}
## Evaluate computing the accuracy
(accuracy  <- sum(true_label[-train_sample] == y_pred[-c(1:n)])/
   (length(true_label) - n))
```
